---
title: "Clustering_Dimension_Reduction"
author: "QD"
output: html_document
---
##Diverging color pallete for 27 individuals
```{r}
c30 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown","indianred1","darkblue","firebrick4","yellowgreen"," wheat4"
)
```


## Dimension reduction plots to see if trends can be observed for MDRO positive/negative samples. Perform at genus level
##Start with PCoA
```{r}
pcoa_genus <- ordinate(genus_005_rel_samples, method='PCoA', distance = 'bray')
pcoa_MDRO_status<-plot_ordination(genus_005_rel_samples, pcoa_genus, color="MDRO_cultured", title='PCoA (Bray-Curtis)') + geom_point(size=3)+xlab("PC1 [22.0%]")+ylab("PC2 [19.3%]")+scale_color_manual(values=c30)+stat_ellipse(type="norm",linetype=2)+labs(color="MDRO cultured")
```
## New figure 4 for revision. This also includes stability (to account for repeated measures)
```{r}
beta_diversity<-ggarrange(pcoa_MDRO_status,Ever_colonized_stability,labels=c("A","B",ncol=1,nrow=2))
ggsave(file="Fig4_Beta_Diversity.svg", plot=beta_diversity, width=12, height=8,dpi=1600)
```

## Intra-individual approach, compare groups with first negative then positive sample. This figure and the one below did not end up in the manuscript, but feel free to have a look at it.
```{r}
genus_005_rel_samples_transient_pre<-subset_samples(genus_005_rel_samples,Transient_colonization_pre=="pre colonisation"|Transient_colonization_pre=="colonisation")
pcoa_genus <- ordinate(genus_005_rel_samples_transient_pre, method='PCoA', distance = 'bray')
pcoa_transient_colonization_pre<-plot_ordination(genus_005_rel_samples_transient_pre, pcoa_genus, color="Residentnumber",shape="Transient_colonization_pre", title='PCoA (Bray-Curtis)')+geom_point(size=3)+scale_color_manual(values=c30)+labs(color="Resident number")+labs(shape="Transient colonisation status")+xlab("PC1 [30.1%]")+ylab("PC2 [18.6%]")
pcoa_transient_colonization_pre
```

## Now compare people first positive then negative
```{r}
genus_005_rel_samples_transient_post<-subset_samples(genus_005_rel_samples,Transient_colonization_post=="post colonisation"|Transient_colonization_post=="colonisation")
pcoa_genus <- ordinate(genus_005_rel_samples_transient_post, method='PCoA', distance = 'bray')
pcoa_transient_colonization_post<-plot_ordination(genus_005_rel_samples_transient_post, pcoa_genus, color="Residentnumber",shape="Transient_colonization_post", title='PCoA (Bray-Curtis)')+geom_point(size=3)+scale_color_manual(values=c30)+labs(color="Resident number")+labs(shape="Transient colonisation status")+xlab("PC1 [38.0%]")+ylab("PC2 [14.4%]")
pcoa_transient_colonization_post
```

