---
title: "Epidemiology"
author: "QD"
output: html_document
---
##Check how many ESBL MDROs are there
```{r}
xtabs(~ESBL, data=metadata_epi)
xtabs(~MDRO_Type_Sample_Based, data=metadata_epi) ##So we have 27 MDROs in total, 13 non-ESBL MDROs and 14 ESBL-MDROs. Of ESBL-positives, 10 are E.coli, 3 are E. cloacae and 1 is a non-koseri Citrobacter. All non-ESBL MDROs are E-coli. When calculating the percentages we come to the following
MDRO_percentage<-(27/93)*100
ESBL_positives_percentage_total<-(14/93)*100
ESBL_positives_percentage_MDROs<-(14/27)*100
unique_residents<-length(unique(metadata_epi$Residentnumber))
xtabs(~C_difficile_at_present, data=metadata_epi) ## No C. difficile was seen in any patient
xtabs(~Ever_Colonized+Residentnumber,data=metadata_epi) ## 12 residents were positive on at least 1 time point, so 15 were never colonized
MDRO_percentage_Ever_Colonized<-(12/27)*100
xtabs(~MDRO_cultured+Sex,data=metadata_epi)
xtabs(~Proton_pump_inhibitor_at_present,data=metadata_epi)
percentage_PPI<-(63/92)*100 ##As from 1 sample PPI use was unknown
xtabs(~Antibiotic_use_at_present,data=metadata_epi)
percentage_present_AB_use<-(4/93)*100
xtabs(~Antibiotic_use_in_past_2_months,data=metadata_epi)
percentage_past_2_months_AB_use<-(16/93)*100
xtabs(~Incontinence_urinary_OR_faecal,data=metadata_epi)
percentage_incontinence_at_present<-(68/93)*100
xtabs(~Ever_Colonized,data=metadata_epi)
count_feces<-as.data.frame(xtabs(~Sample_type+Residentnumber,data=metadata_epi)) ##Liz indicated it would be good to include how many residents have 2, 3 or 4 feces samples
table(count_feces$Freq) ## 3 residents 2 samples, 9 residents 3 samples and 15 residents 4 samples
xtabs(~ESBL+Residentnumber,data=metadata_epi) ## 6 different residents
percentage_residents_with_ESBL<-(6/27)*100
xtabs(~MDRO_cultured+Residentnumber+Time_point,data=metadata_epi)
##Liz also noted that we should write the percentage of E. colis of our MDRO
percentage_E_coli_MDRO<-(22/27)*100
## Now check which residents were positive at all timepoints of which they had samples
metadata_epi$MDRO_cultured<-as.factor(metadata_epi$MDRO_cultured)
ggplot(metadata_epi)+
  aes(x=Time_point,y=Residentnumber,fill=MDRO_cultured,color=MDRO_cultured)+
  geom_point(size=3) ##So only R003 and R004 are positive at all time points. 
MDRO_always_positve<-(2/27)*100
##also include percentages of colonized residents, which residents were colonized on 1 time point, which ones at multiple time points
percentage_colonized_once<-(4/12)*100
percentage_colonized_more_than_once<-(8/12)*100
xtabs(~Ever_Colonized+Residentnumber,data=metadata_epi)
xtabs(~MDRO_cultured+Time_point,data=metadata_epi)
prevalence_timepoint1<-(4/19)*100
prevalence_timepoint2<-(10/25)*100
prevalence_timepoint3<-(7/24)*100
prevalence_timepoint4<-(6/25)*100
metadata_epi$Time_point_prevalence<-metadata_epi$Time_point
metadata_epi$Time_point_prevalence<-as.factor(metadata_epi$Time_point_prevalence)
metadata_epi$Time_point_prevalence<-plyr::revalue(metadata_epi$Time_point_prevalence,c("1"="1 (21.1%)","2"="2 (40%)","3"="3 (29.2%)","4"="4 (24%)"))
##Extra figure for supplementary to show per resident MDRO pos/negative over time. Also add prevalence in % at each time point
metadata_epi$MDRO_cultured <- factor(metadata_epi$MDRO_cultured, levels = c(0,1), labels = c("No","Yes"))

MDRO_cultured_overview<-ggplot(metadata_epi)+
  aes(x=Time_point_prevalence,y=Residentnumber,fill=MDRO_cultured,color=MDRO_cultured)+
  geom_point(size=3)+
  scale_fill_manual(values=c("dodgerblue2", "#E31A1C"))+
  scale_color_manual(values=c("dodgerblue2", "#E31A1C"))+
  theme(legend.title = element_text(size = 14))+
  theme(legend.text=element_text(size=14))+
  theme(axis.text=element_text(size=14))+
  theme(axis.title=element_text(size=16))+
  xlab("Time point and MDRO prevalence in %")+
  ylab("Resident number")+
  labs(fill="MDRO cultured")+
  labs(color="MDRO cultured")

ggsave(file="Fig1_MDRO_cultured_overview.svg", plot=MDRO_cultured_overview, width=12, height=10,dpi=1600)
##Lastly, on reviewer's request, check whether there is a difference in mdro colonization rate between individuals included and excluded in our study
included_excluded<-read_excel("Included_Excluded_residents.xlsx")
rownames(included_excluded)<-included_excluded$...1
chisq.test(included_excluded[,c(2:3)]) ##Not significant,p=0.26
```
##As only variables with at least 10 events will be further used for epidemiological analysis, first filter these out. 
```{r}
xtabs(~Ward, data=metadata_epi) ## Too many wards with less than 10 samples, so delete this variable for further analysis
xtabs(~Building, data=metadata_epi)
xtabs(~Ward_type, data=metadata_epi)
xtabs(~Beds_per_room, data=metadata_epi) ## Only 7 samples with 2 beds per room, so delete 
xtabs(~Toilet, data=metadata_epi) ## Only 7 samples with shared toilets, so delete
xtabs(~Location_prior_nursinghome, data=metadata_epi) ## 3 categories with less than 10 samples, so delete. Do check this quickly in a table to make sure there is not an obvious difference which could be missed by leaving out this variable
xtabs(~Location_prior_nursinghome+MDRO_cultured, data=metadata_epi) ## No difference between being at home or in a nursing home as previous location and risk of MDRO. So can leave this one out of analysis for sure
xtabs(~Hospital_admittance_past_two_months, data=metadata_epi) ## Only 3 samples with hospital admittance in past 2 months, so delete
xtabs(~Desoriented, data=metadata_epi)
xtabs(~Mobility, data=metadata_epi) ##Only 8 triple chair, so delete
xtabs(~Urinary_catheter_at_present, data=metadata_epi)
xtabs(~Pressure_ulcer_wound, data=metadata_epi) ## Only 8 with yes, so delete
xtabs(~Other_wound, data=metadata_epi)
xtabs(~Urine_incontinence, data=metadata_epi)
xtabs(~Faecal_incontinence, data=metadata_epi)
xtabs(~Incontinence_urinary_OR_faecal, data=metadata_epi)
xtabs(~Bile_disease_in_medical_history, data=metadata_epi) ## Only 7, so delete
xtabs(~Urinary_tract_infection_in_medical_history, data=metadata_epi)
xtabs(~Myocardial_infaction_in_medical_history, data=metadata_epi) ## Only 4 with yes, so delete
xtabs(~Kidneyfailure_in_medical_history, data=metadata_epi) ## Only 9 with yes, so delete
xtabs(~Heart_failure_in_medical_history, data=metadata_epi) ## Only 3 with yes, so delete
xtabs(~Hemiplegia_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~Leukemia_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~Stroke_in_medical_history, data=metadata_epi)
xtabs(~Lymphoma_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~Dementia_in_medical_history, data=metadata_epi)
xtabs(~Cancer_in_medical_history, data=metadata_epi)
xtabs(~VRE_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~MDRO_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~MRSA_in_medical_history, data=metadata_epi) ## Only 3 with yes, so delete
xtabs(~COPD_in_medical_history, data=metadata_epi) ## Only 8 with yes, so delete
xtabs(~Liverdisease_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~Connective_tissue_disease_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~AIDS_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~Diabetes_in_medical_history, data=metadata_epi)
xtabs(~Stomach_ulcer_in_medical_history, data=metadata_epi) ## None with yes, so delete
xtabs(~Bowel_disease_in_medical_history, data=metadata_epi) ## Only 3 with yes, so delete
xtabs(~Hypertension_in_medical_history, data=metadata_epi)
xtabs(~Bone_fracture_in_medical_history, data=metadata_epi)
xtabs(~Antibiotic_use_at_present, data=metadata_epi) ## Only 4 with yes, so delete
xtabs(~Antibiotic_use_in_past_2_months, data=metadata_epi)
xtabs(~Proton_pump_inhibitor_at_present, data=metadata_epi)
xtabs(~Diarrhoea_at_present, data=metadata_epi) ## Only 1 sample, so delete
xtabs(~C_difficile_at_present, data=metadata_epi) ## None with yes, so delete
xtabs(~Hospital_admittance_past_year, data=metadata_epi)
##Throw out all variables in which for each category not at least 10 events were observed
metadata_epi_excluded_less_10_events<-dplyr::select(metadata_epi, -c(Ward,Beds_per_room,Toilet,Location_prior_nursinghome,Hospital_admittance_past_two_months,Mobility,Pressure_ulcer_wound,Bile_disease_in_medical_history,Myocardial_infaction_in_medical_history,Kidneyfailure_in_medical_history,Heart_failure_in_medical_history,Hemiplegia_in_medical_history,Leukemia_in_medical_history,Lymphoma_in_medical_history,VRE_in_medical_history,MDRO_in_medical_history,MRSA_in_medical_history,COPD_in_medical_history,Liverdisease_in_medical_history,Connective_tissue_disease_in_medical_history,AIDS_in_medical_history,Stomach_ulcer_in_medical_history,Bowel_disease_in_medical_history,Antibiotic_use_at_present,Diarrhoea_at_present,C_difficile_at_present))

##On Ed's request, perform univariate testing on Pressure_ulcer_wound and Kidneyfailure_in_medical_history
logistic <- glm(MDRO_cultured ~ Pressure_ulcer_wound, data=metadata_epi, family="binomial")
summary(logistic) 
logistic <- glm(MDRO_cultured ~ Kidneyfailure_in_medical_history, data=metadata_epi, family="binomial")
summary(logistic) 
```
##Now convert variables into necessary (e.g. class for MDRO_cultured)
```{r}
metadata_epi_excluded_less_10_events$Building <- as.factor(metadata_epi_excluded_less_10_events$Building)
metadata_epi_excluded_less_10_events$Desoriented <- factor(metadata_epi_excluded_less_10_events$Desoriented, levels = c(0,1), labels = c("No", "Yes"))
metadata_epi_excluded_less_10_events$Urinary_catheter_at_present <- factor(metadata_epi_excluded_less_10_events$Urinary_catheter_at_present, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Other_wound <- factor(metadata_epi_excluded_less_10_events$Other_wound, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Urine_incontinence <- factor(metadata_epi_excluded_less_10_events$Urine_incontinence, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Faecal_incontinence <- factor(metadata_epi_excluded_less_10_events$Faecal_incontinence, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Incontinence_urinary_OR_faecal <- factor(metadata_epi_excluded_less_10_events$Incontinence_urinary_OR_faecal, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Urinary_tract_infection_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Urinary_tract_infection_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Stroke_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Stroke_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Dementia_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Dementia_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Cancer_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Cancer_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Diabetes_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Diabetes_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Hypertension_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Hypertension_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Bone_fracture_in_medical_history <- factor(metadata_epi_excluded_less_10_events$Bone_fracture_in_medical_history, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Antibiotic_use_in_past_2_months <- factor(metadata_epi_excluded_less_10_events$Antibiotic_use_in_past_2_months, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Proton_pump_inhibitor_at_present <- factor(metadata_epi_excluded_less_10_events$Proton_pump_inhibitor_at_present, levels = c(0,1), labels = c("No","Yes"))
metadata_epi_excluded_less_10_events$Hospital_admittance_past_year <- factor(metadata_epi_excluded_less_10_events$Hospital_admittance_past_year, levels = c(0,1), labels = c("No","Yes"))
#metadata_epi_excluded_less_10_events$MDRO_cultured <- factor(metadata_epi_excluded_less_10_events$MDRO_cultured, levels = c(0,1), labels = c("No","Yes"))
```
##Now perform univariate testing on all variables passing the 10 events criterium
```{r}
str(metadata_epi_excluded_less_10_events)
logistic <- glm(MDRO_cultured ~ Sex, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant, but since it is sex, will include in multivariate anyway
logistic <- glm(MDRO_cultured ~ Building, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Borderline not signifcant (p=0.057)
logistic <- glm(MDRO_cultured ~ Desoriented, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Urinary_catheter_at_present, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant, but include in multivariate based on expert opinion
logistic <- glm(MDRO_cultured ~ Other_wound, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Urine_incontinence, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Faecal_incontinence, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Incontinence_urinary_OR_faecal, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Urinary_tract_infection_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Borderline not signifcant (p=0.057)
logistic <- glm(MDRO_cultured ~ Stroke_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Dementia_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Cancer_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Diabetes_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Hypertension_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Significant, include in multivariate
logistic <- glm(MDRO_cultured ~ Bone_fracture_in_medical_history, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Significant, include in multivariate
logistic <- glm(MDRO_cultured ~ Antibiotic_use_in_past_2_months, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Significant, include in multivariate
logistic <- glm(MDRO_cultured ~ Proton_pump_inhibitor_at_present, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Not significant at all
logistic <- glm(MDRO_cultured ~ Hospital_admittance_past_year, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic) ## Significant, include in multivariate
```
##Now move to multivariate logistic regression
```{r}
logistic <- glm(MDRO_cultured ~ Sex+Urinary_catheter_at_present+Hypertension_in_medical_history+Bone_fracture_in_medical_history+Antibiotic_use_in_past_2_months+Hospital_admittance_past_year, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(logistic)
car::vif(logistic) ## Check colinearity, values above 5 indicate highly correlated variables. Since all variables are below 2, there is no real colinearity.
```

## It was indicated by the reviewer that our approach of standard logistic regression was not correct, due to the repeated measures design, which completely correct. Therefore, we employ instead the GEE Logistic Regression. We can then use the same workflow as for the original LR (first univariable LR, then significant + 'likely clinical variables' in the multivariable). These are also the results as reported in our paper.
```{r}
##geeglm needs MDRO cultured to be numeric (0 or 1)
metadata_epi_excluded_less_10_events$MDRO_cultured<-as.character(metadata_epi_excluded_less_10_events$MDRO_cultured)
metadata_epi_excluded_less_10_events$MDRO_cultured<-plyr::revalue(metadata_epi_excluded_less_10_events$MDRO_cultured,c("No"="0","Yes"="1"))
metadata_epi_excluded_less_10_events$MDRO_cultured<-as.numeric(metadata_epi_excluded_less_10_events$MDRO_cultured)
metadata_epi_excluded_less_10_events$Time_point<-as.factor(as.character(metadata_epi_excluded_less_10_events$Time_point))
metadata_epi_excluded_less_10_events$Residentnumber<-as.factor(metadata_epi_excluded_less_10_events$Residentnumber)

geeglm_result<-geeglm(MDRO_cultured ~ Sex,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Building,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Desoriented,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Urinary_catheter_at_present,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Other_wound,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Urine_incontinence,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Faecal_incontinence,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Incontinence_urinary_OR_faecal,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Urinary_tract_infection_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Stroke_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Dementia_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Cancer_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Diabetes_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Hypertension_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Bone_fracture_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Antibiotic_use_in_past_2_months,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
#geeglm_result<-geeglm(MDRO_cultured ~ Proton_pump_inhibitor_at_present,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
#summary(geeglm_result) ## As one missing for PPIs, select data frame without the missing row
geeglm_result<-geeglm(MDRO_cultured ~ Proton_pump_inhibitor_at_present,id = Residentnumber, data = metadata_epi_excluded_less_10_events[-81,], family = "binomial")
summary(geeglm_result)
geeglm_result<-geeglm(MDRO_cultured ~ Hospital_admittance_past_year,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
```
## obtain effect size and CI for the 3 significant variables
```{r}
geeglm_result<-geeglm(MDRO_cultured ~ Bone_fracture_in_medical_history,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
print(tidy(geeglm_result,conf.int = TRUE))
geeglm_result<-geeglm(MDRO_cultured ~ Antibiotic_use_in_past_2_months,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
print(tidy(geeglm_result,conf.int = TRUE))
geeglm_result<-geeglm(MDRO_cultured ~ Hospital_admittance_past_year,id = Residentnumber, data = metadata_epi_excluded_less_10_events, family = "binomial")
summary(geeglm_result)
print(tidy(geeglm_result,conf.int = TRUE)) ## These numbers are converted into log odds in the paper.
```
## Multivariable GEE logistic regression
```{r}
gee_multivariable <- geeglm(MDRO_cultured ~Sex+Urinary_catheter_at_present+Bone_fracture_in_medical_history+Antibiotic_use_in_past_2_months+Hospital_admittance_past_year, id=Residentnumber, data=metadata_epi_excluded_less_10_events, family="binomial")
summary(gee_multivariable)
print(tidy(gee_multivariable,conf.int = TRUE))
## Can still interpret the VIF from the original logistic regression, so no need to recompute this.
```
## Just zoom in on bone fracture in medical history, as quite a stringe finding
```{r}
metadata_epi_bone_fracture<-subset(metadata_epi_excluded_less_10_events,Bone_fracture_in_medical_history=="Yes")
xtabs(~Hospital_admittance_past_year+Antibiotic_use_in_past_2_months,data=metadata_epi_bone_fracture)
metadata_epi_no_bone_fracture<-subset(metadata_epi_excluded_less_10_events,Bone_fracture_in_medical_history=="No")
xtabs(~Hospital_admittance_past_year+Antibiotic_use_in_past_2_months,data=metadata_epi_no_bone_fracture)
xtabs(~Hospital_admittance_past_year+Antibiotic_use_in_past_2_months+Bone_fracture_in_medical_history,data=metadata_epi_excluded_less_10_events)
```

